%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%     PREAMBLE     %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article}

%Define Margins using Geometry Package
\usepackage[top=1.0in,
bottom=1.0in,
right=1.0in,
left = 1.0in]{geometry}


%math
\usepackage{mathtools}


%Set up links and internal references
\usepackage[colorlinks=true,linkcolor=blue, urlcolor=blue]{hyperref} %hide the ugly red boxes
\usepackage[noabbrev]{cleveref} %don't abbreviate ``figure'', etc.
\usepackage{url} %for urls

%Remove natural indentation for itemize and enumerate environments
\usepackage{enumitem} %package to control itemize/enumerate behavior
\setlist[itemize]{leftmargin=*} %for itemize
\setlist[enumerate]{leftmargin=*} %for enumerate
%Swap out the itemize symbol for an N-dash rather than a bullet (does not require enumitem package)
\def\labelitemi{--}

\usepackage{multicol} %Allow for two columns in the middle of a paper. 


%Set up fancy header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
%Fancy Header Content
\fancyhead[L]{ME EN 497R}
\fancyhead[C]{}
\fancyhead[R]{Design Optimization Assignment 3: Final Report}
%Fancy Footer Content
\fancyfoot[L,C]{} %make bottom left and center empty
\fancyfoot[R]{\thepage}

%Center section headings
\usepackage{sectsty}
\subsectionfont{\centering}
%Remove section numbering
\setcounter{secnumdepth}{0}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%     END PREAMBLE     %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%BEGIN Document Environment
\begin{document}
	
\section{Part I: Draft and Review}

This assignment is comprised of two parts, the first of which is to produce a complete draft and submit it for formal review by graduate students in the FLOW lab other than your assigned mentor.
	
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%      Technical Tasks      %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Technical Tasks: Improved Optimization}

You again will have seen or received feedback on potential areas of improvement for your optimization.
So again, complete the following:

\begin{enumerate}[label=\alph*.]
	\item Identify at least 3 (but likely more) areas of improvement for your optimization.
	\item Address each of your identified areas of improvement.
\end{enumerate}



	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%      Writing Tasks      %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Writing Tasks: Results, Conclusion, and Abstract}

Complete the following writing tasks:

\begin{enumerate}[label=\alph*.]
	\item Complete a full draft of your results section, including well-designed plots and thoughtful discussion.  
	\item With the main content of your paper completed, write the conclusion and abstract sections of your paper.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%      Research Skills      %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Research Skills: Draft and Review}
	
Complete the following:
\begin{enumerate}[label=\alph*.]
	\item Ask 2 graduate students in the FLOW Lab, who are not your graduate student mentor, to review your penultimate draft of your final report.
	\item Write a brief document (bullets are good) compiling the feedback as well as describing your actions to address the feedback (or why you didn't).
	\item Create a ``Diff'' document comparing your penultimate and final drafts of your final report.
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%      Final Submission      %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Part II: Final Submission}

Your final submission should be a complete and polished final draft of your semester final technical report.
It should include all the improvements made up to this point as well as improvements based on the feedback you received in the first part of this assignment.
You will be graded on completeness and quality of your final report.
	
	
	
\end{document}