%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%     PREAMBLE     %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article}

%Define Margins using Geometry Package
\usepackage[top=1.0in,
bottom=1.0in,
right=1.0in,
left = 1.0in]{geometry}


%math
\usepackage{mathtools}


%Set up links and internal references
\usepackage[colorlinks=true,linkcolor=blue, urlcolor=blue]{hyperref} %hide the ugly red boxes
\usepackage[noabbrev]{cleveref} %don't abbreviate ``figure'', etc.
\usepackage{url} %for urls

%Remove natural indentation for itemize and enumerate environments
\usepackage{enumitem} %package to control itemize/enumerate behavior
\setlist[itemize]{leftmargin=*} %for itemize
\setlist[enumerate]{leftmargin=*} %for enumerate
%Swap out the itemize symbol for an N-dash rather than a bullet (does not require enumitem package)
\def\labelitemi{--}

\usepackage{multicol} %Allow for two columns in the middle of a paper. 


%Set up fancy header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
%Fancy Header Content
\fancyhead[L]{ME EN 497R}
\fancyhead[C]{}
\fancyhead[R]{Rotor Design - Panel Method Assignment}
%Fancy Footer Content
\fancyfoot[L,C]{} %make bottom left and center empty
\fancyfoot[R]{\thepage}

%Center section headings
\usepackage{sectsty}
\sectionfont{\centering}
%Remove section numbering
\setcounter{secnumdepth}{0}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%     END PREAMBLE     %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%BEGIN Document Environment
\begin{document}
	
	\section{Background}
	
	Airfoils are the cross sections of wings and rotors, so airfoil performance directly affects the performance of any lifting object.
	A simple way to analyze airfoils is by using a \textit{panel method}. 
	For this assignment, you will be utilizing a code produced by students in the FLOWLab called Xfoil.jl.
	
	
	\section{Assignment}

	\begin{enumerate}
		\item Start a new branch on your repository. Name it something relevant to the project. Create issues for each of the following 9 steps of this assignment. Close them with a comment as you finish. each step. 
		\item Read  through the \href{https://en.wikipedia.org/wiki/Aerodynamic_potential-flow_code}{Wikipedia article} on \textit{Aerodynamic potential-flow code.}  Define words and include them in a dictionary that you'll include in an appendix in your report.  Include images to illustrate meaning where applicable. Include equations where applicable to clarify and add meaning. 
		\item Complete the examples given in the Xfoil.jl documentation. Take notes on how the functions are used as you will be using them. 
		\item Explore the effect of airfoil angle of attack on airfoil lift, drag, and moment.
		\item Compare data collected from XFoil to published data (experimental or other). 
		\item Explore the effect of airfoil thickness and camber on airfoil lift, drag., and moment.
		\item Explore the effect of Reynolds number on airfoil lift, drag, and moment.
		\item Write a report (paper) on your methods, results, and takeaways as described in the course syllabus. You should include discussion on what you learned steps 1-7.  Focus on the relationships found steps 4-7. 
		\begin{itemize}
			\item Use the IMRAD format.
			\item Use the provided AIAA conference paper template.
			\item Comment all of the packages in the preamble so you know what they are doing. 
		\end{itemize}
		\item Submit your code and paper via a pull request as described in the course syllabus.
	\end{enumerate}
	
	\bigskip
	
	Here are some words of use that you may want to include in your appendix dictionary:
	
\begin{multicols}{2}
\begin{itemize}
    \item Coefficient of Drag, $C_D$
    \item Coefficient of Lift, $C_L$
    \item Coefficient of Moment, $C_M$
    \item Angle of Attack, $\alpha$
    \item Airfoil Polar
    \item Stall
    \item Chord, $c$
    \item Camber
    \item Airfoil Thickness
    \item Freestream Velocity, $V_\infty$
    \item Reynolds Number, $Re$
    \item Mach Number, $M$
\end{itemize}
\end{multicols}
	
	
	\section{Useful Resources}
	\begin{multicols}{2}
	\begin{itemize}
    		\item \href{https://flow.byu.edu/Xfoil.jl/stable/}{Xfoil.jl Documentation}
    		\item \href{https://dl2.boxcloud.com/d/1/b1!_lom972XNub0HBof1p6FP6KGBb_4tdyvhy5Kb7zl3ld8RIwqlXJndIfGWS2uuEH8qQKhu4oSjIUuztdO0lewCVo__3JyzkW7BMtoCmXh-mj-FgFbpgFQGjKY1W1Mi2mNdgHi1OThVWCKpbtWpwvhD5oeeiOktPg5vSWtl9S3w6SwA0cx8m7S76J2AdIDnGehinA4wTExMuozauk_dMGIhvVKjRlXqEesfp8dYdMxLx7dUtaaqhgh2QEIj4qHnSiHBnvEXL73tQm6d409fRUzb0eZ81cqabFEw_Lt2lPqgRaQnBSlt0NtFB0uZX1roFW3gpcIyBQEMkRwnqQy4r8FLWk5JG-DmTJKsdY4yc_CgUIsKUGN3B4XSU2u1eDqeFKwtj_euudjv3XHq3JyjAUNI2Bd0887Py2wZrgnNA62RtsAvJQAgfvb3Rjj01yinXrZO3Sh7vgzhFNvm08RTtGVAJ8dKhMjJ_gTpcV2Xo3xp18u-9bJvhrJJO3kBgVXswyYu4UHhhSWwaY3J6kABAf1nsNIHybIi6Tc6o2vXdFGyaoFPmTSgxOu9oXHbfksSLolNLNbVi3LMoLAtxSUULaASUe4pqcF1UL9VsKbTXAhU3QkMxAm5dvNxgMgjmgw1e_K6kFfnsODFtAtTIxMwH3Ycxqs7hhWh8DjR3SJCvnk045UFSyhFL439ngh0O7DtI7kZPx84c-aIMT7vAd2eKOii-YnLFOMYNtU9yLQLVhkVDIrOcneMZqU78IACJvLD3yvaA4D72rnWw78Yx7oH0975bxcKK3XmaD3mnqcwVKKZp9Eb1s0dwVsZ48MIG5KfMG_NQglf4OYsRHxsNSy1CzDI9W2YQwenv_Hi0urX0RkpggfXaoLTRqclLxSssphDgi-z02KKcj6TLMqZ-JjoqSecKYNMSa0btiXrtMBfZkIfVSWEAPzkfv2WcJKbxSDE4ny2wxDyG07AcX3DvXOC7HI6J7GCWCaDpRlb6_aY8bfFrQtDN0oETsksJb6IzPa6MWVWln5kV8UQxM9NNHDXS4luZTXFJqUPeNWzTjTKfuuigfKEmy3p9PRHKvLMHt9EhEaVywSxAHer02V_XlCa6ZyLbFGgfreDnUwvS72sr-F0V73y_gLDGd9aSNe0kadPSmanZwXmtv3TJRMudduzOC-PQISkY2Jk_3l-ZfMzAPTpD7-Uojlj-gDCiXyxpjncuEQXgtKlA2LhABZ0_oGFIIeAxG_ZMrdpK3s39XrONytYijpSqrkJRx3bF3gPU2WaLrFvpC2shsDwqIIw1uIwBO7fxjnepjnqqb2F0NvOFOddbYSefYou00FbGXpONMRmaE0ZpUs-KhE97kdOCcnnMfsz7N5q7GgqUuX8MzNR7Phtg18q6GXXnozAMFE9Yg8yz53204qd7w./download}{ME 515 Textbook : Chapter 2 Sections 5 \& 6}
    		\item \href{http://web.mit.edu/drela/Public/web/xfoil/xfoil_doc.txt}{XFoil Documentation}
    		\item \href{https://www.google.com/}{Google}
	\end{itemize}
	\end{multicols}
	
	
	
	
	
	
\end{document}